### 2014-06-27 2/literature_review.tex
auto

The parameters that describe the polarization ellipse are: 
\begin{equation}
\tan (\theta ) = \frac{E_y^0}{E_x^0}
\end{equation}
with
	$0 \leq \theta \leq \pi/2$. 
The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
\begin{equation}
\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
\end{equation}
with
	$0 \leq \Psi < \pi$. 
The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
\begin{equation}
\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
\end{equation}
with
	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$

@@

The Stokes vector is then defined as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation}

@@

Although speckle has been extensively studied for decades, speckle reduction remains one of the major issue in SAR imaging process. 
Many reconstruction filters have been proposed, and they can be classified into two main categories: 
	Weighted Least-Square Error de-speckling using the speckle model; 
	and maximum a posteriori (MAP) de-speckling using the product model. 
In this section, various different approaches to SAR speckle filtering are reviewed.
%The famous Lee, Kuan, and Frost ˆÄÅé‡§èÅlters in the ˆÄÅé‡§èÅrst category provide MMSE reconstructions based on measured local statistics.
%In the second category, diˆÄÅé‡§èÄerent scene distributions are used: Gaussian, Gamma, and parameter-based distributions.

>>>>

The parameters that describe the polarization ellipse are:
  the intensity orientation angle $\theta$,
  the ellipticity angle $\Psi$,
  and the orientation angle $\chi$.
They are defined as:
\begin{equation}
\tan (\theta ) = \frac{E_y^0}{E_x^0}
\end{equation}
with
	$0 \leq \theta \leq \pi/2$. 
The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
\begin{equation}
\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
\end{equation}
with
	$0 \leq \Psi < \pi$. 
The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
\begin{equation}
\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
\end{equation}
with
	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$

@@

The Stokes vector is then defined as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation}
where $\Re$ and $\Im$ respectively denotes the real and imaginary parts of a complex number.

@@

Although speckle has been extensively studied for decades, speckle reduction remains one of the major issue in SAR imaging process. 
Many reconstruction filters have been proposed, and they can be classified into two main categories: 
	Weighted Least-Square Error de-speckling using the speckle model; 
	and maximum a posteriori (MAP) de-speckling using the product model. 
In this section, various different approaches to SAR speckle filtering are reviewed.
A recent review of this topic is available in \cite{Argenti_GRSM_2013}.
%The famous Lee, Kuan, and Frost ˆÄÅé‡§èÅlters in the ˆÄÅé‡§èÅrst category provide MMSE reconstructions based on measured local statistics.
%In the second category, diˆÄÅé‡§èÄerent scene distributions are used: Gaussian, Gamma, and parameter-based distributions.

### 2014-06-27 4/polsar.tex
auto

Over a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constants.
Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explanation that, 
  in the original POLSAR domain, a multiplicative speckle noise pattern is present.
At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
  the logarithmic transformation converts this into a more familiar additive noise.

@@

%TODO: add p-value here for 
\begin{figure}[bth!]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast (p-value HH-HV=0.9182)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast (p-value=0.9254)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.
Each histogram plots the signal(s) under investigation against its probabilistic distribution across the patch,
  with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.  
}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}

>>>>

Over a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constants.
Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explanation that, 
  in the original POLSAR domain, a multiplicative speckle noise pattern is present.
At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
  the logarithmic transformation converts this into a more familiar additive noise.
\footnote{
  As replied to the thesis' Examiners: Since the original domain is multiplicative, the range of small value is quite limited ($|C_v|$ ranges from 0 to 1).
  The log transformed domain not only changes the nature of the noise from multiplicative to addtive,
    it also gives this ``small'' range a much wider space ($\ln{|C_v|}$ ranges from $-\infty$ to 0).
  In other words, it helps to expand the ``narrow'' distribution depicted in Eqn. \ref{eqn:determinant_distribution} to become another distribution whose shape does not depend on $\Sigma$, as depicted in Eqn. \ref{eqn:log_determinant_distribution}
}

@@

%TODO: add p-value here for 
\begin{figure}[bth!]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion (p-value HH-HV=0.8942)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast (p-value HH-HV=0.9182)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion (p-value=0.8806)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast (p-value=0.9254)]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.
Each histogram plots the signal(s) under investigation against its probabilistic distribution across the patch,
  with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.  
}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}

### 2014-06-27 6/conclusional_discussion.tex
auto

Since the full POLSAR data is multi-dimensional and the proposed models are scalar,
  by their own definition, they are not perfect.
They inherently suffer from a loss of dimension.  
%The
%                proposed scalar models for POLSAR also have limitations.
%It
%                calls for a dimensional reduction operation, which is
%                probably not lossless.
Thus
                while the determinant of POLSAR covariance matrix is
                said to be "highly representative", it is definitely not
                fully representative of the data.
This restricts the use of the models to a class of porblem where a single scalar decision, ranking, sorting or classification answer is required from the complex dataset.
They however, are hopefully the most practical way to answer some common types of commonly asked questions such as:
  ``what is the best speckle filter for the given data set?'' or
  ``what type of surface does a region of interest belong to?''.
On the other hand, the proposed models might not be very useful in applications,
  where the relationship among each dimensional component is used to make further inferences.

>>>>

Since the full POLSAR data is multi-dimensional and the proposed models are scalar,
  by their own definition, they are not perfect.
They inherently suffer from a loss of dimension.  
%The
%                proposed scalar models for POLSAR also have limitations.
%It
%                calls for a dimensional reduction operation, which is
%                probably not lossless.
Thus
                while the determinant of POLSAR covariance matrix is
                said to be "highly representative", it is definitely not
                fully representative of the data.
This restricts the use of the models to a class of problems where a single scalar decision, ranking, sorting or classification answer is required from the complex dataset.
They, however, are the most practical way to answer some commonly asked questions such as:
  ``what is the best speckle filter for the given data set?'' or
  ``what type of surface does a region of interest belong to?''.
On the other hand, the proposed models might not be very useful in applications,
  where the relationship among each dimensional component is used to make further inferences.
